Object Naming in Language and Vision: A Survey and a New Dataset

### 2020-03-12 papers/LREC2020/background.tex
LREC paper, small change in table 1
LREC paper: polish intro, adding refs; a few questions remain
small changes here and there.

The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \refexp{dog}'', ``the white \refexp{dog} to the left'').
Since an object is simultaneously a member of multiple categories (e.g., a young beagle belongs to the categories \cat{dog}, \cat{beagle}, \cat{animal}, \cat{puppy}, \cat{pet}, etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be called by different names \cite{brown1958shall,murphy2004big}.

Seminal work by \newcite{rosch1976basic} inspired a taxonomic view of object naming, in which names exhibit a preferred level of specificity or abstraction called the ``entry-level'' \cite{jolicoeur1984pictures}. 
This typically corresponds to an intermediate level of specificity (basic level,\ e.g., \refexp{bird}, \refexp{car}), as opposed to more generic (super-ordinate,\ e.g., \refexp{animal}, \refexp{vehicle}) or more specific categories (sub-ordinate,\ e.g., \refexp{sparrow}, \refexp{convertible}).
However, less prototypical members of basic level categories tend to be instead identified with sub-ordinate categories (e.g., a penguin is typically called \refexp{penguin} and not \refexp{bird}; \newcite{jolicoeur1984pictures}).

%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers adopt their naming choices to the context and, hence, are flexible with respect to the chosen level of specificity \cite{olson1970language,rohde2012communicating,graf2016animal}.
%Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating,graf2016animal}.
For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-ordinate category (e.g., \textsl{rottweiler}, \textsl{beagle}) is potentially preferred by speakers. The effect of such distractor objects on the production of referring expressions has been widely examined in the language generation community \cite{krahmer:2012}, though not specifically for object naming. We believe that our new dataset provides an interesting resource for tackling this question.
%, though additional factors such as cost or saliency also come into play \cite{graf2016animal,clark1983common}.

The purely taxonomic view on naming has also been criticized in work on object organization, which found that many objects of our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}. 
This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.\ \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
We provide tentative evidence that cross-classification is indeed relevant for naming variation, and that the taxonomic axis is not the most frequent source of variation in our data.

@@

In Computer Vision, object recognition is often modeled as a classification task where state-of-the-art systems localize and classify objects into thousands of different categories  \cite{googlenet,ILSVRC15}. 
Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} ontology, and typically assume a single ground-truth label. 
The construction of ImageNet was set up as a two-stage procedure: (i) images for given categories in the ontology were automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}. 
Recently, \newcite{pont2019natural} have argued for annotation of object labels using free form text though here this free vocabulary is then mapped to a set of underlying classes.
Thus, even though object recognition benchmarks do provide images of objects and categories, they generally do not provide what we are interested in in this work, namely natural names of objects.

\subsection{Object Naming in L\&V}

Previous work in L\&V has collected and used data sets where annotators produced free and natural utterances for a given image. 
Moreover, these data sets typically record utterances that are more complex than a single word, such as image captions \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, visual dialogues \cite{das2017visual,vries2017guesswhat} or image paragraphs \cite{krause2017hierarchical}. While object names occur in all of these data sets, they are not necessarily marked up and linked to the corresponding image regions. The overview in Section \ref{sec:survey} will discuss corpora where the grounding of names to regions for objects is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.

Our new collection, ManyNames, focusses on object names in isolation and is substantially more controlled than common L\&V data sets. This controlled collection procedure allowed us to elicit many annotations for the same object from different annotators, resulting in a data set that is amenable to studying variation and preferences in naming systematically and on a large scale.

\begin{table*}[htb]
  \centering
  \begin{tabular}{lrrrrr}
    \toprule
    &   RefCOCO/+  &  Flickr30kE &           VG &      VGmn &        MN \\
    \midrule
    \# objects & 50,000 & 243,801 & 3,781,232 & 25,315 & 25,315 \\
    naming vocab size &  5,004 &  10,423 &   105,441 &  1,061 &  7,970 \\
    av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
    \% objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
    av. types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
    \bottomrule
  \end{tabular}
  \caption{Overview statistics for different data sets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.\label{tab:compare}}
\end{table*}

>>>>

The act of naming an object amounts to that of picking out a nominal to be employed to refer to it (e.g., ``the \word{dog}'', ``the white \word{dog} to the left'').\cs{rephrase}
Since an object is simultaneously a member of multiple categories (e.g., a young beagle belongs to the categories \cat{dog}, \cat{beagle}, \cat{animal}, \cat{puppy}, \cat{pet}, etc.), all the various names that lexicalize these constitute a valid alternative, meaning that the same object can be called by different names \cite{brown1958shall,murphy2004big}.

Seminal work by \newcite{rosch1976basic} inspired a taxonomic view of object naming, in which names exhibit a preferred level of specificity or abstraction called the ``entry-level'' \cite{jolicoeur1984pictures}. 
This typically corresponds to an intermediate level of specificity (basic level,\ e.g., \word{bird}, \word{car}), as opposed to more generic (super-ordinate,\ e.g., \word{animal}, \word{vehicle}) or more specific categories (sub-ordinate,\ e.g., \word{sparrow}, \word{convertible}).
However, less prototypical members of basic level categories tend to be instead identified with sub-ordinate categories (e.g., a penguin is typically called \word{penguin} and not \word{bird}; \newcite{jolicoeur1984pictures}).

%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
While the traditional notion of entry-level categories suggests that objects tend to be named by a \textit{single} preferred concept, research on pragmatics has found that speakers adopt their naming choices to the context and, hence, are flexible with respect to the chosen level of specificity \cite{olson1970language,rohde2012communicating,graf2016animal}.
%Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases \cite{rohde2012communicating,graf2016animal}.
For example, in presence of more than one dog, the name \textsl{dog} is ambiguous and a sub-ordinate category (e.g., \word{rottweiler}, \word{beagle}) is potentially preferred by speakers. The effect of such distractor objects on the production of referring expressions has been widely examined in the language generation community \cite{krahmer:2012}, though not specifically for object naming. We believe that our new dataset provides an interesting resource for tackling this question.
%, though additional factors such as cost or saliency also come into play \cite{graf2016animal,clark1983common}.

The purely taxonomic view on naming has also been criticized in work on object organization, which found that many objects of our daily lives are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}. 
This \textit{cross-classification} occurs, for instance, with food categories which can be taxonomy-based (e.g.,~\word{meat, vegetable}) or script-based (e.g.,~\word{breakfast, snack}).
We provide tentative evidence that cross-classification is indeed relevant for naming variation, and that the taxonomic axis is not the most frequent source of variation in our data.

@@

In Computer Vision, object recognition is often modeled as a classification task where state-of-the-art systems identify objects by classifying them into thousands of different categories  \cite{googlenet,ILSVRC15}. 
Current recognition benchmarks use labels and images from the ImageNet \cite{imagenet_cvpr09} ontology, and typically assume a single ground-truth label. 
The construction of ImageNet was set up as a two-stage procedure: (i) images for given categories in the ontology were automatically collected by querying search engines, (ii) crowd-workers then verified whether each candidate image is an instance of the given category.
Other data collection efforts for object labels also used a predefined vocabulary and asked annotators to mark all instances of these categories in a set of images \cite{mscoco,OpenImages}.\cs{double-check latter} 
Recently, \newcite{pont2019natural} have argued for annotation of object labels using free form text though here this free vocabulary is then mapped to a set of underlying classes.
Thus, even though object recognition benchmarks do provide images of objects and categories, they generally do not provide what we are interested in in this work, namely natural names of objects.

\subsection{Object Naming in L\&V} 
Previous work in L\&V has collected and used datasets where annotators produced free and natural utterances for a given image. 
These datasets typically record utterances that are more complex than a single word, such as image captions \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic}, referring expressions \cite{Kazemzadeh2014,mao15,Yu2016}, visual dialogues \cite{das2017visual,vries2017guesswhat} or image paragraphs \cite{krause2017hierarchical}. 
While object names occur in all of these datasets, they are not necessarily marked up and linked to the corresponding image regions. The overview in Section \ref{sec:survey} will discuss corpora where the grounding of names of objects to their regions is given, as in the case of \vgenome \cite{krishna2016visualgenome}, or where it can be easily derived, as in the case of referring expressions.

Our new collection, ManyNames, focusses on object names in isolation and is substantially more controlled than common L\&V datasets. This controlled collection procedure allowed us to elicit many names for the same object from different annotators, resulting in a dataset that is amenable to  studying systematically and on a large scale the core phenomena of object naming, viz. naming variation and preferences.\cs{rephrase}

\begin{table*}[htb]
  \centering
  \begin{tabular}{lrrrrr}
    \toprule
    &   RefCOCO/+  &  Flickr30kE &           VG &      VGmn &        MN \\
    \midrule
    \# objects & 50,000 & 243,801 & 3,781,232 & 25,315 & 25,315 \\
    name vocabulary size &  5,004 &  10,423 &   105,441 &  1,061 &  7,970 \\
    av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
    ratio of objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
    av. name types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
    \bottomrule
  \end{tabular}
  \caption{Overview statistics for different datasets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.\label{tab:compare}}
\end{table*}

### 2020-03-12 papers/LREC2020/conclusion.tex
small changes here and there.

For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object categorization and naming.
Crucially, evaluations in these tasks assume that object identification is possible based on the bounding box; beyond showing that this is not always the case, our data can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case), or really off.

@@

With respect to naming variation, our current data supports the prediction in theoretical research on object naming that there will often be a preferred (entry-level) name for a given visually presented object.
It tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a hierarchical view, which has been dominant in the psycholinguistic and computational literature; (c) there is high variability in agreement across instances within the same domain.
The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation. With prototypical, idealized pictures of the sort used in traditional studies (see Figure\ \ref{fig:cake}), this observation would not be possible.

>>>>

For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object recognition and naming.
Crucially, evaluations in these tasks assume that object identification is possible based on the box; beyond showing that this is not always the case, our data can be used to assess whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case), or really off.

@@

%With respect to naming variation, our
Our current data supports the prediction in theoretical research on object naming that there will often be a preferred (entry-level) name for a given visually presented object.
It tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a hierarchical view, which has been dominant in the psycholinguistic and computational literature; (c) there is high variability in agreement across instances within the same domain.
The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation. With prototypical, idealized pictures of the sort used in traditional studies (see Figure\ \ref{fig:cake}), this observation would not be possible.

### 2020-03-12 papers/LREC2020/data-collection.tex
small changes here and there.

\begin{table*}[htp]
	\small
	\centering
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
		\toprule
		vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
		\midrule
		train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
		car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
		plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
		airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
		motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
		% truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
		% boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
		% jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
		% aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
		% van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
		\bottomrule
	\end{tabular}
	\caption{Overview of the ManyNames dataset: Top 5 VG names for each domain (number of instances in parentheses).\label{tab:overview_dataset1}}
\end{table*}

@@

We take data from \vgenome~(VG) because its dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,\ the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
Moreover, its object names are linked to WordNet synsets \cite{fellbaum1998wordnet}, which affords analysis possibilities that we will exploit in Section~\ref{sec:analysis} below.
% The object names were obtained from the region descriptions (see Section~\ref{sec:vg-survey}).
Note that, as common in Computer Vision, objects in \vg images are localized as bounding boxes, as shown in Figure~\ref{fig:cake} (left).% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

@@

%Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al. as basis.
We selected images from seven domains: \domain{animals\_plants}, \domain{buildings}, \domain{clothing}, \domain{food}, \domain{home}, \domain{people}, \domain{vehicles}. 
They are all based on McRae et al.'s  \cite{mcrae2005semantic} feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories, except for \domain{people}, which we added because it is a very frequent category in \vg and a very prominent category for humans.
% We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\domain{animals}, \domain{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
% We added the \domain{person} category because it is very frequent category in \vgenome.

Within each domain, we aimed at collecting instances at different taxonomic levels to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \textit{dog} and \textit{cow} are both mammals, but \textit{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.\ \domain{home}).
Instead, we defined a set of 52 synsets (listed in Table~\ref{tab:overview_dataset2}) that we used to collect object instances from \vg, as follows.

First, to create our synset set, we chose those \vg synsets that match or subsume the object classes in the McRae norms, and cover different names in \vg.
%which \vg objects get diverse names.
For example, \vg instances subsumed by McRae's \textsl{dog} were named \textsl{dog, beagle, greyhound, bulldog}, etc., while McRae's \textsl{duck}, \textsl{goose}, or \textsl{gull} did not have name variants in \vg, so we kept \textsl{dog} and \textsl{bird} (which subsumes \textsl{duck}, \textsl{goose}, or \textsl{gull}) as collection synsets.
%\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}

We then retrieved all VG images depicting an object whose name matches a word in these collection synsets or in those subsumed by them. We refer to the names obtained as \textit{seeds} ($450$\ in total).
%\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds. This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as explained next.
Table~\ref{tab:overview_dataset1} shows the top 5 \vg names in each of the domains. 
%\gbt{If someone feels like it: It'd be good to use small caps for domains throughout, and also to have the same (alphabetical?) order for all domains in all tables.}

@@

To elicit object names, we set up a crowdsourcing task on Amazon Mechanical Turk (AMT).
In initial pilot studies, we found object identification via bounding boxes to be problematic.
In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (for instance, for a box around a jacket, the man wearing it).
We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning images with unclear boxes or occluded objects via an initial collection round in which we allowed workers to mark such cases.
Figure~\ref{fig:instructions1} shows the task instructions for this first round, in which 9 workers annotated each image.

%We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images.
After the first round, and based on the opt-out annotation, we kept images that met all the following conditions (thresholds were estimated via manual inspection): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most 17\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vg name.
This yielded $25,596$ images (we discarded $5,497$).
We then did 3 more collection rounds, obtaining a total of 36 images per object.
Figure~\ref{fig:instructions2} shows the instructions for these rounds; they were accompanied by a FAQ solving common issues. 
We shuffled the set of images per task between rounds, and workers could only participate in one round, to avoid workers annotating an instance more than once.
Overall $841$\ workers took part in the data elicitation, with a median of  $261$\ instances \mbox{($\textrm{range}=[9,17K]$)} per worker.

>>>>

\iffalse
\begin{table*}[htp]
	\small
	\centering
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
		\toprule
		vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
		\midrule
		train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
		car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
		plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
		airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
		motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
		% truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
		% boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
		% jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
		% aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
		% van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
		\bottomrule
	\end{tabular}
	\caption{Overview of the ManyNames dataset: Top 5 VG names for each domain (number of instances in parentheses).\label{tab:overview_dataset1}}
\end{table*}
\fi

\begin{figure*}[htp]
	\centering
	\includegraphics[height=.8\columnwidth]{figures/distr_imgs-per-domain_VG.png}
	\caption{Overview of the number of images and names per domain in ManyNames.}
	\label{fig:overview_dataset1}
\end{figure*}

@@

We take data from \vgenome~(VG) because its dense annotations of images can be beneficial to analyze the factors affecting naming (e.g.,~the category or salience of other objects), and how these impact the modeling of natural language in L\&V.
\vg suits our purpose of collecting names for naturalistic instances of common objects, as it has images of varying complexity, with close-ups as well as images with many objects.
Moreover, its object names are linked to WordNet synsets \cite{fellbaum1998wordnet}, which allows for analysis possibilities that we will exploit in Section~\ref{sec:analysis}.
% The object names were obtained from the region descriptions (see Section~\ref{sec:vg-survey}).
Note that, as common in Computer Vision, objects in \vg images are localized as bounding boxes, as shown in Figure~\ref{fig:cake} (left).% 
\footnote{We use image and object interchangeably in the following, since we only selected one target object per image (i.e., each object and image in VG is chosen at most once).}

@@

%Criteria: From CV: select images depicting objects with relatively frequent names; From CogSci: select objects which have been frequently studied in cognitive science/psychological norming studies; we chose McRae et al. as basis.
We selected images from seven domains: \domain{animals\_plants}, \domain{buildings}, \domain{clothing}, \domain{food}, \domain{home}, \domain{people}, \domain{vehicles}. 
They are all based on McRae et al.'s~\shortcite{mcrae2005semantic} feature norms, a dataset widely used in Psycholinguistics that comprises common objects of different categories, except for \domain{people}, which we added because it is a very frequent category in \vg and a very prominent category for humans.
% We start from the concepts of McRae et al.'s feature norms (REF), which are common objects of different categories (e.g.,~\domain{animals}, \domain{furniture}) and, as such, have a high overlap with standard datasets of object norming studies (REFS).
% We added the \domain{person} category because it is very frequent category in \vgenome.

Within each domain, we aimed at collecting instances at different taxonomic levels to cover a wide range of phenomena, but this is not straightforward because ontological taxonomies do not align well with the lexicon (for instance, \word{dog} and \word{cow} are both mammals, but \word{dog} has many more common subcategories), and most domains are not organized in a clear taxonomy in the first place (e.g.,~\domain{home}).
Instead, we defined a set of $52$~synsets (listed in Table~\ref{tab:overview_dataset2}) that we used to collect object instances from \vg, as follows.

First, to create our synset set, we chose those \vg synsets that match or subsume the object classes in the McRae norms, and cover different names in \vg.
%which \vg objects get diverse names.
For example, \vg instances subsumed by McRae's \word{dog} were named \word{dog, beagle, greyhound, bulldog}, etc., while McRae's \word{duck}, \word{goose}, or \word{gull} did not have name variants in \vg, so we kept \word{dog} and \word{bird} (which subsumes \word{duck}, \word{goose}, or \word{gull}) as collection synsets.
%\gbt{Just to clarify: we also collected objects named \textsl{duck}, \textsl{goose}, or \textsl{gull}, right? Not only \textsl{bird}?}

We then retrieved all VG images depicting an object whose name matches a word in these collection synsets or in those subsumed by them. We refer to the names obtained as \textit{seeds} ($450$~in total).
%\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\word{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$~instances for seeds with up to $800$~objects, and up to $1$K~instances for larger seeds. This yielded a dataset of $31,093$~instances, which was further pruned during annotation, as explained next.
Table~\ref{tab:overview_dataset1} shows the top $5$~\vg names in each of the domains. 
%\gbt{If someone feels like it: It'd be good to use small caps for domains throughout, and also to have the same (alphabetical?) order for all domains in all tables.}

@@

To elicit object names, we set up a crowdsourcing task on Amazon Mechanical Turk (AMT).
In initial pilot studies, we found object identification via bounding boxes to be problematic.
In some cases, the bounding box was not clear; in others, AMT workers named objects that were more salient than the one signaled by the box (e.g.,~for a box around a jacket, the man wearing it).
We took special care of minimizing this issue in two ways: Specifying the instructions such that workers pay close attention to what object is being indicated in the box, and pruning images with unclear boxes or occluded objects via an initial collection round in which we allowed workers to mark such cases.
Figure~\ref{fig:instructions1} shows the task instructions for this first round, in which $9$~workers annotated each image.

%We eliminated around $5.5$K\ images based on pruning, obtaining the final dataset with $25,596$\ images.
After the first round, and based on the opt-out annotation, we kept images that met all the following conditions (thresholds were chosen by manually inspecting the remaining and discarded instances, respectively, depending on different threshold values): (i) they were not marked as occluded by any subject; (ii) ``Bounding box is unclear'' was marked at most twice; (iii) at most~$17$\% of elicited names were in plural form (to remove cases where the bounding box contains several objects); (iv) the most frequent elicited name is of the same domain as the \vg name.
This yielded $25,596$~images (we discarded~$5,497$).
We then did ~3~more collection rounds, obtaining a total of $36$~annotations per object.
Figure~\ref{fig:instructions2} shows the instructions for these rounds; they were accompanied by a FAQ solving common issues. 
We shuffled the set of images per task between rounds, and workers could only participate in one round, to avoid workers annotating an instance more than once.
Overall $841$~workers\footnote{Participation was restricted to residents of the UK, USA, Canada, New Zealand, and Australia.} took part in the data elicitation, with a median of  $261$~instances \mbox{($\textrm{range}=[9,17K]$)} per worker.

### 2020-03-12 papers/LREC2020/lrec2020naming.tex
small changes here and there.

\abstract{
People choose particular names for objects, such as \word{dog} or \word{puppy} for a given dog.
Object naming has been studied in Psycholinguistics, but has received relatively little attention in Computational Linguistics.
We review resources from Language and Vision that could be used to study object naming on a large scale, discuss their shortcomings, and create a new dataset that affords more opportunities for analysis and modeling.
Our dataset, ManyNames, provides 36 name annotations for each of 25K objects in images selected from VisualGenome.
We highlight the challenges involved and provide a preliminary analysis of the ManyNames data showing that there is a high level of agreement in naming, on average. At the same time, the average number of name types associated with an object is much higher in our dataset than in existing corpora for Language and Vision, such that ManyNames provides a rich resource for studying phenomena like hierarchical variation (\word{chihuahua} vs.\ \word{dog}), which has been discussed a lot in the theoretical literature, and other less well studied phenomena like cross-classification (\word{cake} vs.\ \word{dessert}).
% may not be the main driver of diversity in naming behavior, \cs{sounds weird:}at least in our setup.\cs{in naming behavior on real-world objects (?)}
 \\ \newline \Keywords{object naming, language and vision, computer vision} }

@@

\section{Object Names in Existing L\&V resources}
\label{sec:survey}
\input{survey}

@@

%\section{Acknowledgements}

% Place all acknowledgements (including those concerning research grants and
% funding) in a separate section at the end of the article.

>>>>

\abstract{
People choose particular names for objects, such as \word{dog} or \word{puppy} for a given dog.
Object naming has been studied in Psycholinguistics, but has received relatively little attention in Computational Linguistics.
We review resources from Language and Vision that could be used to study object naming on a large scale, discuss their shortcomings, and create a new dataset that affords more opportunities for analysis and modeling.
Our dataset, ManyNames, provides 36 name annotations for each of 25K objects in images selected from VisualGenome.
We highlight the challenges involved and provide a preliminary analysis of the ManyNames data showing that there is a high level of agreement in naming, on average. At the same time, the average number of name types associated with an object is much higher in our dataset than in existing corpora for Language and Vision, such that ManyNames provides a rich resource for studying phenomena like hierarchical variation (\word{chihuahua} vs.\ \word{dog}), which has been discussed at length in the theoretical literature, and other less well studied phenomena like cross-classification\cs{Should we keep this term? (@GBT cf. discussion with A. Maedebach)} (\word{cake} vs.\ \word{dessert}).
% may not be the main driver of diversity in naming behavior, \cs{sounds weird:}at least in our setup.\cs{in naming behavior on real-world objects (?)}
 \\ \newline \Keywords{object naming, language and vision, computer vision} }

@@

\section{Object Names in Existing L\&V Resources}
\label{sec:survey}
\input{survey}

@@

\section{Acknowledgments}
We thank the anonymous reviewers for their comments, and the AMT workers who participated in our crowdsourcing task.  
 This project has received funding from the European Research Council~(ERC) under the European Union's Horizon~2020 research and innovation programme (grant agreement No715154), from the Ramón y Cajal programme~(grant RYC-2015-18907), and by the Catalan government~(SGR 2017 1575).
 % Spanish  State  Research  Agency~(AEI) and  the  European  Regional  Development  Fund~(FEDER, UE) (project PGC2018-094029-A-I00). 
 This paper reflects the authors' view only,  and the EU is not responsible \mbox{for any use that may be made of the information it contains.}
 \hfill \includegraphics[scale=.03]{figures/LOGO_ERC-FLAG_EU_.jpg}
% Place all acknowledgements (including those concerning research grants and
% funding) in a separate section at the end of the article.
